Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-27 paper.tex

            Early neuroimaging workflow engines, such as SPM, are monolithic, 
            thus preventing users from incorporating their custom workflows

        \section{Workflow sharing}\label{sharing}
    \chapter{Performance}\label{performance}
        \section{Filesystems}
            scientific: shared FS such as Lustre, NFS, S3
            big data: mapreduce - HDFS, spark and dask shared or distributed
        \section{Scheduling}
            scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)
        \section{Performance enhancement strategies}
            scientific: not much
            big data: data locality, in memory computing, lazy evaluation
    \chapter{Portability}\label{portability}
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        \section{Provenance Tracking}
        big data frameworks: limited to lineage
        \section{containerization}
    \chapter{Discussion/Conclusion}

>>>>

            Early neuroimaging workflow engines, such as SPM, are monolithic, 
            and therefore, do not provide a mechanism for users to incorporate
            their custom tools. Workflow engines, such as AA, were thus 
            conceived to enable engines such as SPM to be more modular. AA 
            allows users to define their tasks through XML specification. AA's 
            XML tasklist is simply an ordered list of tasks which also includes
            details on analysis-specific parameters. Dependencies are
            inferred by the program through analysis of the module interfaces.
            Module interfaces consist of MATLAB user script and an XML 
            descriptor. The descriptor contains details on the input and output
            data stream types (e.g. epi, structural, dicom\_header) 
            and the desired domain (e.g. study, subject, session). During 
            execution, each task is given its own unique folder to operate on. 
            The engine will copy data to and extract data from this folder.

            LONI and FastR are other examples of workflow engines that use an
            XML interface to describe CLIs. LONI enables generation of the 
            XML-based module interface through its GUI. The module interface
            consists of details on \note{from website} module metadata (e.g.
            authors, package, version, name) and citation information, 
            command-line syntax, parameter and file types, dependencies and 
            output and error handling.

            FastR allows for the definition of workflow modules in both XML and 
            JSON. Module definitions are broken down into two components, 
            \textit{Tool} and \textit{Interface} class. The \textit{Tool} is the
            component that is written in either XML or JSON. It defines three
            components: general metadata, target and interface. General metadata
            consists of details such as name, version and authors. The target, 
            on the other hand, consists of details on the execution environment
            (e.g. operating system, interpreter and binary file). The last 
            component of the \textit{Tool}, the interpreter, provides details on
            the inputs and outputs of the tool (e.g. name, datatype, cardinality
            , location). FastR provides to schemas to validate and convert the 
            \textit{Tool} to a Python object
            : the \textit{Tool} schema and \textit{FastRInterface}. Should these
            schemas not meet the requirements of the user, the user may choose 
            to define their own schema.

            Some workflows do not require module interfaces, as is the case with
            Make.

        \section{Workflow sharing}\label{sharing}
    \chapter{Performance}\label{performance}
        \section{Filesystems}
            scientific: shared FS such as Lustre, NFS, S3
            big data: mapreduce - HDFS, spark and dask shared or distributed
        \section{Scheduling}
            scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)
        \section{Performance enhancement strategies}
            scientific: workflow checkpointing (looking at file hashes)
            big data: data locality, in memory computing, lazy evaluation
    \chapter{Portability}\label{portability}
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        \section{Provenance Tracking}
        big data frameworks: limited to lineage
        \section{containerization}
    \chapter{Discussion/Conclusion}
